The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-27 paper.tex
update

  The AMR base level is covered by $16\times16\times32$ root grids, refined progressively on the plane $z=0$\
  , with the outflow boundary condition.

  \subsubsection{The clumpy, and warm/cold ISM disk}

@@

@@

  Moreover, as the clouds are considered to be thermally unstable\
  when the cloud temperature beyond\
  the critical temperature of the warm atomic phase.\
  We replace the cell density with\
  $\rho_{\text{ismDisk}}T_{\text{ismDisk}}/T_{\text{atmp}}$\
  for a cell temperature greater than the critical value $T_{\text{crit}}$.

  %Doing so, the porosity of the disk can arises,\

@@

\begin{table*}[t]
\raggedright
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                               & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                           &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                           &                                      &                                \\
$v_{\text{halo}}$                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                           &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disk }                &                                           &                                      &                                \\
$z_{0}$                               & Scale height of disk                      & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disk }                    &                                           &                                      &                                \\
$T_{\text{\text{c}}}$                 & Critical temperature of warm atomic phase & $10^{4}$ K                           & \citep{peak-ism-density}       \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                &   N/A                          \\
$\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma$                     & Dispersion of scalar field                & 2.2                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual clump $\sim 100$ pc.
      \item    $\ddag$  $\sigma=$ ....
    \end{tablenotes}
\end{table*}

@@

\subsection{Cold disk}
  We restrict the refinement level is 7 within the cold disk so that\
  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.\

>>>>

@@

  \subsection{The Clumpy Multiphase Interstellar Medium}

@@

%  Moreover, since the clouds are considered to be thermally unstable\
%  when the cloud temperature beyond\
%  the critical temperature of the warm atomic phase,\
%  we replace the cell density as\
%  $\rho_{\text{ismDisk}}T_{\text{ismDisk}}/T_{\text{atmp}}$\
%  when the cell temperature beyond the critical value $T_{\text{crit}}$.

@@

  The AMR base level is covered by $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
  based on the gradient of mass desnity.\
  The highest refinement level is 7 so that the clumps within the disk can be adequately\
  resolved by approximately 30 cells along their diameter, 20 pc.

\begin{table*}[t]
\raggedright
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                               & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                           &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                           &                                      &                                \\
$v_{\text{halo}}$                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                           &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disk }                &                                           &                                      &                                \\
$z_{0}$                               & Scale height of disk                      & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disk }                    &                                           &                                      &                                \\
$T_{\text{\text{c}}}$                 & Critical temperature of warm atomic phase & $10^{4}$ K                           & \citep{peak-ism-density}       \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                & \multicolumn{1}{c}{''}         \\
$\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma$                     & Dispersion of scalar field                & 5.0                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
      \item  $\ddag$ In numerical simulations of turbulence,\
             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free) and compressive (curl-free) forcing,\
             respectively, so that our adopted value of 5 is closer to their solenoidal result.
    \end{tablenotes}
\end{table*}

@@

\subsection{Cold disk}
